Title Text

### 2014-04-01 paper.tex
More writing on the Pull intro

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Lenore M. Mullin}
           {Emeritus Professor\\Department of Computer Science \\
University at Albany, SUNY}
           {lenore@cs.albany.edu}

@@

\begin{figure}
\begin{verbatim}
map :: (a -> b) -> Pull a -> Pull b
map f (Pull ixf l) = Pull (f . ixf) l
\end{verbatim}
\caption{Example functions on pull arrays}
\end{figure}

@@

>>>>

\authorinfo{Josef Svenningsson}
           {Department of Computer Science of Engineering\\Chalmers University of Technology}
           {josef.svenningsson@chalmers.se}
\authorinfo{Lenore M. Mullin}
           {Emeritus Professor\\Department of Computer Science \\
University at Albany, SUNY}
           {lenore@cs.albany.edu}

@@

\begin{figure}
\begin{verbatim}
-- Mapping a function over an array
map :: (a -> b) -> Pull a -> Pull b
map f (Pull ixf l) = Pull (f . ixf) l

-- Apply a binary operation itemwise on two arrays
zipWith :: (a -> b -> c)
        -> Pull a -> Pull b -> Pull c
zipWith f (Pull ixf1 l1) (Pull ixf2 l2)
  = Pull (\i -> f (ixf1 i) (ixf2 i)) (min l1 l2)

-- Takes the n first elements of an array
take :: Int -> Pull a -> Pull a
take n (Pull ixf l) = Pull ixf (min n l)

-- Drops the n first elements of an array
drop :: Int -> Pull a -> Pull a
drop n (Pull ixf l)
  = Pull (\i -> ixf (i + n)) (max (l - n) 0)

-- Rotate an array k steps to the left
rotate :: Int -> Pull a -> Pull a
rotate k (Pull ixf l)
  = Pull (\i -> ixf ((i + k) `mod` l)) l
\end{verbatim}
\caption{Example functions on pull arrays}
\end{figure}

@@

The first uses of Pull arrays used a fixed number of dimensions,
typically either one or two. However, the Repa library introduced a
new expressive notion of higher dimensionality for Push arrays
\cite{keller2010regular}. The number dimensions of an array, referred
to as the \emph{shape}, are determined statically in the type
system. While this might seem very constraining, a key innovation in
Repa is the notion on \emph{shape polymorphism} which makes it
possible to write functions which accepts arrays of any shape. Below
shows the definition of the type of shapes. It is a variation on how
it is represented in Feldspar.

\begin{verbatim}
data Z
data i :. sh

data Shape sh where
  Z :: Shape Z
  (:.) :: Shape tail -> Int -> Shape (tail :. Int)
\end{verbatim}

The first two data declarations introduces new types, \verb!Z! and
\verb!:.!, without any constructors. They are used to create
snoc-lists on the type level, the definition of \verb!Shape!.  The
type \verb!Shape! is a recursive data type with two constructors. The
first constructor \verb!Z! indicates that the shape has zero
dimensions.  The second constructor \verb!:.! adds one dimension to
another shape, and stores how many elements there are in that
dimension. The type \verb!Shape! has a type parameter which is a snoc
list with one element for each dimension.

\begin{verbatim}
data Pull sh a = Pull (Shape sh -> a) (Shape sh)

map :: (a -> b) -> Pull sh a -> Pull sh a
map f (Pull ixf sh) = Pull (f . ixf) sh

zipWith :: (a -> b -> b) -> 
           Pull sh a -> Pull sh b -> Pull sh c
zipWith f (Pull ixf1 sh1) (Pull ixf2 sh2)
  = Pull (\sh -> f (ixf1 sh) (ixf2 sh2))
\end{verbatim}
